Computing volume via non-linear rectangular prisms

### 2019-08-14 Cav2D/article-template.tex
making sure it is synced

\noindent
Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. Let the $A_R$ denote 
the area of $R$. We can approximate $A_R$ with:
\begin{equation}
 \label{eq:caval1}
 A_R \approx \sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
 \end{equation}
Let us verify that this is indeed the case:
 \begin{itemize}
  \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
  \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
  \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
  \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
  \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
 \end{itemize}

\noindent
The aforementioned limit is known as Cavalieri integral and in this paper we denote this integral as follows:

>>>>

\noindent
Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. Let the $A_R$ denote 
the area of $R$. We can approximate $A_R$ with:
\begin{equation}
 \label{eq:caval1}
 A_R \approx \sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
 \end{equation}
Let us verify that this is indeed the case:
 \begin{itemize}
  \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
  \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
  \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
  \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
  \item In the limit the Cavalieri sum (if this limit exists), therefore, approaches the area of $R$.
 \end{itemize}

\noindent
The aforementioned limit is known as the Cavalieri integral and in this paper we denote this integral as follows:
